---
title: "Developing Data Products - courseProjectShinyApp"
author: "Snehal Tapdiya"
date: '2019-01-31'
output: html_document
runtime: shiny
---

### Introduction
This shiny app demonstrates the growth of Orange trees..

### Shiny widget Radio buttons for selecting the type of graph.

```{r echo = FALSE}
radioButtons(inputId = "plotType", label = "Plot type", choices = c("Scatter"="p", "Line"="l"))
```

### Output plot based on selected plot type

```{r echo=FALSE}
library(ggplot2)
data <- Orange
data$Tree <- paste0("Tree ", data$Tree)
output$plot <- renderPlot({
    
    # draw the scatter or line plot based on selected input
    g <- ggplot(data, aes(x=age, y=circumference)) + 
      labs(title = "Orange tree growth plot", x = "Age of tree", y="Circumference of tree")
    
    if (input$plotType == "l") {
      g <- g + geom_line(aes(colour=Tree), size=2)
    } else if (input$plotType == "p") {
      g <- g + geom_point(aes(fill=Tree), shape=24, size=8)
    }
    g
  })

plotOutput("plot", brush = brushOpts(id = "brushPlot"))

```

### Select the area on the plot, and you'll see the output section in sidebar panel will display the data for the selected region on the plot.

```{r brush info, echo=FALSE}
output$orangeOutput <- renderPrint({
    # print tree, age, circumference for selected area
    brushedPoints(data, input$brushPlot, xvar = "age", yvar = "circumference")
  })

```

### Output

```{r echo=FALSE}
verbatimTextOutput("orangeOutput")

```

#### Note : Output section won't display any data until area is not selected on the plot.